### 2014-09-26 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edit
San Francisco: Minor edit to description of fire and simulation timeline

Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifying assumptions were made. One assumption is that the initial couch fire in the basement was specified to start at the beginning of the simulation. The beginning of the simulation ($t=0$) was selected to correspond to an on-scene time of 10:53:00 (see Table~\ref{tab:incident_timeline}). The HRRs for the three primary source fires was prescribed in FDS as follows.

@@

\item The third exterior fuel item included the wood on the basement balcony and siding. To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data about ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes. The results of that study indicate that the HRRPUA for different types of wood is approximately 50~kW/m$^2$.

@@

As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a total height of 5.9~m (19~ft). To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure. The dimensions of the computational domain were 11.5~m (38~ft) by 22~m (72~ft) by 13.6~m (45~ft). A grid resolution of 10~cm (3.9~in) was used, which resulted in a total of approximately 3.4 million computational cells. As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm. Figure~\ref{fig:SMV_exterior_grid} shows the front and rear sides of the structure rendered in Smokeview with the 10~cm mesh.

>>>>

Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifying assumptions were made. One assumption is that the initial couch fire in the basement was specified to start at the beginning of the simulation. The duration of the fire simulation was 9~min (540~s). The beginning of the simulation (0~s) was selected to correspond to an on-scene time of 10:53:00, which was approximately five minutes after the fire department arrived on scene and approximately one minute before the E26 firefighting crew stated that the fire was located below the first floor. The end of the simulation (540~s) was selected to correspond to an on-scene time of 11:02:00, which is the time at which fire suppression operations began (see Table~\ref{tab:incident_timeline}).

The HRRs for the three primary source fires were prescribed in FDS as follows.

@@

\item The third exterior fuel item included the wood on the basement balcony and siding. To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data abotu the ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes. The results of that study indicate that the HRRPUA for different types of wood is approximately 50~kW/m$^2$.

@@

As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a total height of 5.9~m (19~ft). To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure. The dimensions of the computational domain were 11.5~m (38~ft) by 22~m (72~ft) and a height of 13.6~m (45~ft). A grid resolution of 10~cm (3.9~in) was used, which resulted in a total of approximately 3.4 million computational cells. As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm. Figure~\ref{fig:SMV_exterior_grid} shows the front and rear sides of the structure rendered in Smokeview with the 10~cm mesh.
